### 2017-02-15 docs/reports/experiments_MH-DTM/report_mh-dtm.tex
Adjusting the model tuning.

\par The intention of the carried experiments is to identify the optimal settings for the Metropolis--Hastings algorithm application. 
To start with, I have generated a synthetic corpus; the parameters used in the corpus generation will allow to assess the performance achieved in the experiments. The corpus generation parameters are set as follows:
\begin{itemize}
	\item The number of topics: K = 2;
	\item The number of documents (time-slices): T = 20;
	\item The size of vocabulary: V = 10;
	\item The number of words per document t: $N_t \sim \mbox{Pois}(\lambda),\quad \lambda = 1000$.
\end{itemize}
Further, to consider the initial settings of $\alpha_k$ development over documents, $\alpha_0$ is a sine curve and $\alpha_1$ is a cosine curve; the corresponding \textit{softmax} expressions of the curves are illustrated in Figure 1 below.
\begin{figure}[H]
  \centering
  \includegraphics[width=0.5\textwidth]{alpha_initial}
  \caption{The values of $\mu$ used in the generative process.}
  \label{fig:mu}
\end{figure}
Speaking of $\beta$, it was initially predefined and kept constant throughout the dynamic generative process; $\beta$ is illustrated in Figure 2 below.
\begin{figure}[H]
  \centering
  \includegraphics[width=0.5\textwidth]{beta_initial}
  \caption{The values of $\beta$ used in the generative process.}
  \label{fig:beta}
\end{figure}
Note that the latter $\beta$ values were applied to the autoregressive topic model for the $\alpha$ update experiments.
% ___________________________________________________________________

@@

\par The experiment involved $500$ autoregressive iterations and $\sigma^2$ were set to $0.1$. The idea was to tune the model with different values of $\sigma_0$ and $\delta^2$; the choice of different values is illustrated in Figures 3, 4, 5 below.

@@

>>>>

\par The intention of the carried experiments is to identify the optimal settings for the Metropolis--Hastings algorithm application. 
To start with, I have generated a synthetic corpus; the parameters used in the corpus generation will allow to assess the performance achieved in the experiments. The corpus generation parameters are set as follows:
\begin{itemize}
	\item The number of topics: K = 2;
	\item The number of documents (time-slices): T = 20;
	\item The size of vocabulary: V = 10;
	\item The number of words per document t: $N_t \sim \mbox{Pois}(\lambda),\quad \lambda = 1000$.
\end{itemize}
Further, to consider the initial settings of $\alpha_k$ development over documents, $\alpha_0$ is a sine curve and $\alpha_1$ is a cosine curve; the corresponding softmax expressions of the curves, i.e $\mu = \mbox{softmax}(\alpha)$, are illustrated in Figure 1 below.
\begin{figure}[H]
  \centering
  \includegraphics[width=0.5\textwidth]{alpha_initial}
  \caption{The values of $\mu$ used in the generative process.}
  \label{fig:mu}
\end{figure}
Speaking of $\beta$, it was initially predefined and kept constant throughout the dynamic generative process; $\beta$ is illustrated in Figure 2 below.
\begin{figure}[H]
  \centering
  \includegraphics[width=0.5\textwidth]{beta_initial}
  \caption{The values of $\beta$ used in the generative process.}
  \label{fig:beta}
\end{figure}
Note that the latter $\beta$ values were applied to the autoregressive topic model for the $\alpha$ update experiments.
% ___________________________________________________________________

@@

\par For both experiments, the number of autoregressive iterations was set to $500$ and $\sigma^2$ was set to $0.1$. The resulting plots of $\mu$ with different values of $\sigma_0$ and $\delta^2$ are illustrated in Figures 3, 4, 5 below.

@@

\par The second experiment was carried to determine the impact of the $\alpha$ update in recovering the original topic fluctuations in the synthetic corpus. For this reason, the autoregressive part of the dynamic topic was disabled. The topic assignments to the documents of the last iteration are visualised in Figure 6 below.
% ___________________________________________________________________

\section*{Observations}

\par For the last section of this report, I have set some questions to be addressed during next meeting; these are listed below:
\begin{itemize}
	\item In some cases, the larger number of iterations reduced the performance in reproducing the initial $\alpha$;
\end{itemize}
